\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-26 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Première version table 4
Il manque des donnéess.
graphique robustesse séparée

@@

\begin{figure}[htbp]
\caption{Robustness to the separability assumption (year-to-year basis)}
\label{fig:robustesse_non_separe}
\begin{center}
\begin{tabular}{cc}
{\small (a) Air freight} & {\small (b) Vessel freight}\\
\includegraphics[width=3in, height=2in]{graph_robustesse_ns_mp_terme_A_air.pdf}
& \includegraphics[width=3in,height=2in]{graph_robustesse_ns_mp_terme_A_ves.pdf} \\
\includegraphics[width=3in, height=2in]{graph_robustesse_ns_mp_terme_I_air.pdf}
& \includegraphics[width=3in,height=2in]{graph_robustesse_ns_mp_terme_I_ves.pdf} \\

>>>>

\begin{table}[htbp]
	\centering
	\caption{Robustness to the separability assumption (average over the period) - restricted sample}
	\begin{center}
			\input{table4.tex}
	\end{center}
	\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule: for each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows.
			The additive term is expressed in fraction of fas price.}}
	\label{tab:robustness_separability}
\end{table}

@@

\begin{figure}[htbp]
\caption{Robustness to the separability assumption (year-to-year basis)}
\label{fig:robustesse_non_separe}
\begin{center}
\begin{tabular}{cc}
\includegraphics[width=6in, height=4in]{graph_robustesse_ns.jpg}
